\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-22 document/ms.tex
making the catalog its own section
stoopid tex formatting
smaller font in table 7
moar stoopid tex formatting
Added further discussion of Figure 6

To limit the scope of this paper while still demonstrating the applicability
of our method, we search the \kepler\ archival light curves of the brightest
and quietest Sun-like stars for long-period transiting exoplanets.
In this section, we describe the target selection process, the parameter
estimation procedure, and present the catalog of discoveries.

@@

\subsection{Catalog of transit candidates}\sectlabel{catalog}

@@

In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
distributions of our discoveries to the longest-period planet candidates
discovered transiting stars in our target list by the official \kepler\
transit search \citep{Coughlin:2016}.
These histograms do not take uncertainties or detection efficiency into
account so any conclusions based on these plots should be taken with caution.
That being said, the apparent deficit of planets in the period range between
600 and 1000~days cannot be explained by selection effects~--~in fact, the
geometric transit probability exacerbates the signal~--~and should be
investigated more thoroughly.
We postulate three scenarios and expect that the observed effect is the result
of some combination of the three:
\begin{itemize}
{\item the periods of some candidates are overestimated and the missing second
transit occurs in a data gap,}
{\item overestimated stellar densities leading to an overestimate of the
orbital periods and an underestimate of the radii, or}
{\item a physical rise in the frequency of giant planets at long orbital
periods.}
\end{itemize}
The first two scenarios could be confirmed or ruled out by detailed analysis
of each candidate system and follow-up data.
Any result would be physically interesting but a rigorous analysis that is
beyond the scope of this \paper\ would be required to make a conclusive claim.

@@

\section{Empirical search completeness}\sectlabel{completeness}

@@

\begin{floattable}
\begin{deluxetable}{ccccccccc}
\tabletypesize{\footnotesize}
\caption{The predicted masses and radial velocity signals for the candidates
from Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablecomments{The masses and radial velocity amplitudes are estimated based
on the measured radius using a probabilistic mass--radius relation
\citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}

@@

\bibliography{peerless}

>>>>

To limit the scope of this paper while still demonstrating the applicability
of our method, we search the \kepler\ archival light curves of the brightest
and quietest Sun-like stars for long-period transiting exoplanets.
In this section, we describe the target selection process and the parameter
estimation procedure.

@@

\section{Catalog of transit candidates}\sectlabel{catalog}

@@

In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
distributions of our discoveries to the longest-period planet candidates
discovered transiting stars in our target list by the official \kepler\
transit search \citep{Coughlin:2016}.
These histograms do not take uncertainties or detection efficiency into
account so any conclusions based on these plots should be taken with caution.
That being said, the apparent deficit of planets in the period range between
600 and 1000~days cannot be explained by selection effects~--~in fact, the
decreasing geometric transit probability and decreased orbital phase coverage at
longer periods exacerbates the signal~--~and should be
investigated more thoroughly.  The decline at longer periods can be attributed
to the declining transit detection probability.
We postulate three scenarios and expect that the observed effect is the result
of some combination of the three:
\begin{itemize}
{\item the periods of some candidates are overestimated and the missing second
transit occurs in a data gap,}
{\item overestimated stellar densities leading to an overestimate of the
orbital periods and an underestimate of the radii, or}
{\item a physical rise in the frequency of giant planets at long orbital
periods.}
\end{itemize}
The first two scenarios could be confirmed or ruled out by detailed analysis
of each candidate system and follow-up data.
Any result would be physically interesting but a rigorous analysis that is
beyond the scope of this \paper\ would be required to make a conclusive claim.

The difference between the observed radius distributions apparent in Figure \ref{obs-dist}
can be attributed to the drop off in sensitivity of our search at small planet
radius depicted in Figure \ref{completeness}.  The \kepler\ survey, on the other 
hand, has increasing sensitivity to smaller planets due to the addition of multiple 
transits at shorter period.

@@

\newpage
\section{Empirical search completeness}\sectlabel{completeness}

@@

\begin{floattable}
\begin{deluxetable}{ccccccccc}
\tabletypesize{\scriptsize}
\caption{The predicted masses and radial velocity signals for the candidates
from Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablecomments{The masses and radial velocity amplitudes are estimated based
on the measured radius using a probabilistic mass--radius relation
\citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}

@@

\newpage
\bibliography{peerless}
